### 2016-07-14 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
strikeout fixed

The evaluation of creative systems developed by researchers in the field of computational creativity has proven non-trivial. Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}. Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about 'creativity' and what does it constitute?

@@

Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. 
% Currently, no one definition has been adopted as standard, either in everyday use (as evidenced by the dictionary definitions considered below), for research % purposes \cite{rhodes61,taylor88,plucker04defn} or even in legal practice \cite{clifford04,mandel11}, where one would expect a term critical to legal 
% judgements  -- as creativity surely is \cite{feist91,karjala08,schafer15} -- to be precisely and unambiguously defined. 
%
%The difficulty of formulating an adequate definition of creativity in words should not discourage us from the attempt, however  \cite{rhodes61,plucker04defn,kaufman09}. Even if other researchers have been swayed away from this task \cite[for example]{sternberg99a,veale06preface},  care must be taken that we `do not throw out the baby with the bath water just because the water is cloudy' \cite[p. 310]{rhodes61}. Some of the issues concerning the problem of defining creativity have been debated for decades. The following sections consider the need for an explicit and comprehensive definition of creativity and the difficulties researchers encounter in providing one.

\paragraph{\sout{A question of definition?}}

%{\bf \em The next paragraph needs some thought, as it is is still talking about the need for definition. I think Plucker's comments on the original submission might suggest that he feels that this debate has now concluded (and that definition(s) of creativity have been provided. If so, then we need to modify this, at least.)}
\sout{Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research. He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited' \cite[p.87]{plucker04defn} and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding' \cite[p.92]{plucker04defn}. In fact, `Rather than being a strength of the field, as many believe, the lack of a common definition is a major, debilitating weakness. ... we feel that an agreed-on definition is long overdue and has placed the field in a crisis of legitimacy. ... This change in the focus and direction of creativity research is needed if the field is to move from a shadowy past into the forefront of constructive approaches' \cite[p. 93]{plucker04defn}. Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear' \cite[p. 310]{rhodes61}.}

>>>>

The evaluation of creative systems developed by researchers in the field of computational creativity has proven non-trivial. Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}. Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about `creativity' and what does it constitute?

@@

Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. 
% Currently, no one definition has been adopted as standard, either in everyday use (as evidenced by the dictionary definitions considered below), for research % purposes \cite{rhodes61,taylor88,plucker04defn} or even in legal practice \cite{clifford04,mandel11}, where one would expect a term critical to legal 
% judgements  -- as creativity surely is \cite{feist91,karjala08,schafer15} -- to be precisely and unambiguously defined. 
%
%The difficulty of formulating an adequate definition of creativity in words should not discourage us from the attempt, however  \cite{rhodes61,plucker04defn,kaufman09}. Even if other researchers have been swayed away from this task \cite[for example]{sternberg99a,veale06preface},  care must be taken that we `do not throw out the baby with the bath water just because the water is cloudy' \cite[p. 310]{rhodes61}. Some of the issues concerning the problem of defining creativity have been debated for decades. The following sections consider the need for an explicit and comprehensive definition of creativity and the difficulties researchers encounter in providing one. 
\paragraph{\sout{A question of definition?}}
%{\bf \em The next paragraph needs some thought, as it is is still talking about the need for definition. I think Plucker's comments on the original submission might suggest that he feels that this debate has now concluded (and that definition(s) of creativity have been provided. If so, then we need to modify this, at least.)}
\sout{Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research. He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited'} \cite[\sout{p.87}]{\sout{plucker04defn}} \sout{and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding'} \cite[\sout{p.92}]{\sout{plucker04defn}}. \sout{In fact, `Rather than being a strength of the field, as many believe, the lack of a common definition is a major, debilitating weakness. ... we feel that an agreed-on definition is long overdue and has placed the field in a crisis of legitimacy. ... This change in the focus and direction of creativity research is needed if the field is to move from a shadowy past into the forefront of constructive approaches' }\cite[\sout{p. 93}]{\sout{plucker04defn}}. \sout{Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear' }\cite[\sout{p. 310}]{\sout{rhodes61}}.
